Cluster Paper

### 2015-03-31 ms.tex
added IFU figure
added this test figure and a junk caption.

>>>>

\begin{figure} 
	\includegraphics[width=0.49\textwidth]{f01.pdf} 
	\caption{The ICD as a function of galaxy stellar mass. Individual galaxies are shown as gray points. The galaxies are then binned together by stellar mass in bins of 0.5 dex (except for the highest mass bin which is 1.0 dex) beginning with $\mathrm{Log~M}/\Msol =8.5$. The upper and lower quartiles of ICD are indicated by the blue boxes. The median of each bin is indicated by the red line. The upper and lower black bars show the 95th and 5th percentiles. The ICD for galaxies in our sample is low for low stellar masses, peaks in the intermediate stellar masses, and returns to low values at high stellar masses.} \label{fig:icd_vs_mass} 
\end{figure}
